---
title: "Lista 4"
output:
  html_document:
    df_print: paged
  word_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## 3 Comparing two proportions

3. Comparing two proportions
The following table gives the records of accidents in 1998 compiled by the Department of Highway Safety and Motor Vehicles in Florida.

<style type="text/css">
.tg  {border-collapse:collapse;border-spacing:0;}
.tg td{font-family:Arial, sans-serif;font-size:14px;padding:10px 5px;border-style:solid;border-width:1px;overflow:hidden;word-break:normal;border-color:black;}
.tg th{font-family:Arial, sans-serif;font-size:14px;font-weight:normal;padding:10px 5px;border-style:solid;border-width:1px;overflow:hidden;word-break:normal;border-color:black;}
.tg .tg-0pky{border-color:inherit;text-align:left;vertical-align:top}
</style>
<table class="tg">
  <tr>
    <th class="tg-0pky"></th>
    <th class="tg-0pky" colspan="2">Injury</th>
  </tr>
  <tr>
    <th class="tg-0pky">Safety</th>
    <th class="tg-0pky">Fatal</th>
    <th class="tg-0pky">Nonfatal</th>
  </tr>
  <tr>
    <td class="tg-0pky">None</td>
    <td class="tg-0pky">1601</td>
    <td class="tg-0pky">162,527</td>
  </tr>
  <tr>
    <td class="tg-0pky">Seat Belt</td>
    <td class="tg-0pky">510</td>
    <td class="tg-0pky">412,368</td>
  </tr>
</table>

Denote the number of accidents and fatalities when no safety equipment
was in use by nN and yN, respectively. Similarly, let nS and yS denote the
number of accidents and fatalities when a seat belt was in use. Assume
that yN and yS are independent with yN distributed as binomial(nN, pN)
and yS distributed as binomial(nS, pS). Assume a uniform prior is placed
on the vector of probabilities (pN, pS).
a) Show that pN and pS have independent beta posterior distributions.


```{r warning=FALSE, message=FALSE}
library(BayesianFirstAid)
fatal<-c(1601,510)
total<-c(1601+162527,510+412368)

fit<-bayes.prop.test(fatal,total)
plot(fit)




```


b) Use the function rbeta to simulate 1000 values from the joint posterior
distribution of (pN, pS).


```{r }
samples<-as.data.frame(fit)
head(samples)

samples<-samples[1:1000,1:2]

head(samples)

```
c) Using your sample, construct a histogram of the relative risk pN/pS.
Find a 95% interval estimate of this relative risk.

```{r }

samples$risk<-samples$theta1/samples$theta2

hist(samples$risk)

library(gmodels)
ci(samples$risk,conf.level = 0.95)


```


d) Construct a histogram of the difference in risks pN − pS.

```{r }

samples$diff<-samples$theta1-samples$theta2

hist(samples$diff)

```

e) Compute the posterior probability that the difference in risks exceeds
0.

```{r echo=FALSE}



